Robust self-testing of large entanglement with constant alphabet

### 2019-04-23 Draft/draft.tex
Honghao: finished section 3

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
the finite-dimensional representation of a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,\uc) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
the linear system game ($H\ux = \uc$) has
\begin{enumerate}
	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$,
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
We follow a similar approach to construct our ideal strategy. However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime with primitive root $r$,
and this correlation is denoted by $C(\dr{r})$.  \carl{Be more precise --- we are constructing
such a correlation for any $d$ which has $2, 3,$ or $5$ as a primitive root.}
\hf{One part of $C(\dr{r})$ is produced by the optimal quantum strategy of a linear system game, denoted by $\LS$.}
In this section, we introduce the linear system game which tests a key relation that should be satisfied by 
Alice and Bob's observables.

In Slofstra's seminal work~\cite{slofstra2017} embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be reproduced from the
combination of the equations of the linear system game. The special relation $xyx^{-1} = y^2$ inspired 
our work.
\hf{We generalize this relation and make he solution group of $\LS_r$ the embedding of the 
following group}
\begin{align}
	\Pg_r= \langle u, o : uou^{-1} = o^r \rangle, \text{ for } r \in \N.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uou^{-1} = o^r$.  
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with the numbers of variables, $\nr := 17r + 73$, 
	and the number of equations, $\mr =15r + 61$, where each equation involves $3$ variables.
	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

In the later parts of the paper, we use $\nr$ and $\mr$ to refer to the size of $\LS_r$.
The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ have arbitrary order. 
The product of the generators $x_1$ and $x_2$ from the solution group of $\LS_r$ plays the role 
of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
of the generator $u$ in $\Pg_r$.   \carl{It's reasonable to make a couple informal statements
at the beginning of a section, but you shouldn't be making
such vague statements at this point.  Everything said at this point in the section should have a precise mathematical
meaning.}
As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
$x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
\begin{align}
	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^r.
\end{align}
Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
the key relation that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^r\ket{\psi}, 
\end{align}
and similarly on Bob's side.
If we denote the unitary corresponding to the generator $u$ of $\Pg_r$ by $U$ and the unitary
corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
$UXU\ct \ket{\psi} = X^r \ket{\psi}$.
The special property of $U$ and $X$ is summarized in the following lemma.

\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/r}{i},
	\end{align}
	where $d$ is an odd prime number with primitive root $r$,
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^r$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
\carl{We shouldn't be making extra assumptions that are not stated in the lemma.  This looks to me more like
a definition of the variables $\{ k_i \}$, rather than an assumption.}
The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

%\begin{align}
%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
%\end{align}
%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
%by the following relations
%\begin{align}
%\label{eq:sim}
%	u_x x u_x = x^2, \quad
%	u_z z u_z = z^2.
%\end{align}
%Consequently, the $d$ dependency of $\G$ comes from constraints imposed by other components of the game,
%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
%relation $xzx^{-1}z^{-1} = \J$.
%
%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
%\begin{align}
%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
%\end{align}
%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
%we can verify that 
%\begin{align}
%	U_xU_z = \1 = U_zU_x,
%\end{align}
%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
%In the end, we define $\Pg_{\LS}$ by
%\begin{equation}
%\begin{aligned}
%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
%\end{aligned}
%\end{equation}
%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.

>>>>

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
the finite-dimensional representation of a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,\uc) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
the linear system game ($H\ux = \uc$) has
\begin{enumerate}
	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$,
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
We follow a similar approach to construct our ideal strategy. However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.

@@

%=======================================
\section{The linear constraint test}
\label{sec:lct}
%=======================================
In this section, we introduce a linear constraint test that is satisfied by our correlation.
The linear constraint test is designed to enforce relations that should be satisfied by 
Alice and Bob's observables and it is inspired by 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be derived from the
combination of the equations of the linear system game. Then he showed the difference between exact representations
and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group}
\begin{align}
	G = \langle u, o : uou^{-1} = o^r \rangle, 
\end{align}
for some $r \in \N$ into a linear constraint test.

%------------------------------------------------------------------------
\subsection{The embedding of $G$}
%------------------------------------------------------------------------
The main result of this subsection is summarized in the following theorem.
\begin{theorem}
	The relation $uou^{-1} = o^r$ can be embedded in a linear constraint test which has
	$n(r) := 18r+86$ variables and $m(r) := 16r + 72$ equations, where each equation has $3$ variables.
\end{theorem}
We prove this by constructing the solution group $\Gamma$ of the linear constraint test. 
We also prove some properties of the generators of $\Gamma$ along the way.

We embed $G$ into $\Gamma$ in three steps and introduce two intermediate groups $G_0$ and $G_1$, which are defined below.
\begin{definition}
	The presentation of $G_0$ has order-$2$ generators:
	\begin{align}
		\{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5
	\end{align}
	and relations:
	\begin{align}
	&u_3 = u_2o_1u_2 && u_4 = u_2o_2u_2 \\
	&u_5 = u_1u_3u_1 && o_2 = u_1u_4u_1\\
	&u_5 = o_1 o_r o_1,
	\end{align}
	and when $r$ is even
	\begin{align}
	&o_{1+2j} = o_1o_{2j}o_1 && o_{2+2j} = o_2o_{1+2j}o_2&& \text{ for } j = 1 \dots r/2 - 1;
	\end{align}
	when $r$ is odd
	\begin{align}
	&o_3 = o_2o_1o_2 &&
	 o_{2+2j} =o_1o_{1+2j}o_1 && o_{3+2j} = o_2o_{2j+2}o_2 &&\text{ for } j = 1 \dots (r-3)/2.
	\end{align}
\end{definition}
\begin{proposition}
	The group $G_1$ embeds the relation 
	\begin{align}
		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
	\end{align}
	for any $ j \in \N$.
\end{proposition}
The proof follows the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017}
\begin{proof}
	We prove it by induction.
	Direct calculation gives us that
	\begin{align} 
		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
	=& u_5 o_2\\
	=& o_1o_ro_1 o_2.
	\end{align}
	Then substituting the definitions of $o_k$ for $k = r \dots 3$ gives us the case for $j=1$.

	Now assume the statement is true for $j = n$, then when $j = n+1$
	\begin{align}
		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
		 =& (o_1o_2)^{r^{n+1}},
	\end{align}
	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$ and $o_1o_2$.
	Hence, the statement is true.
\end{proof}
To better characterize all the conjugation relations above and simplify the form of $G_1$
and make the introduction of $G_2$ easier, we relabel $u_i$ and $o_i$'s
as $a_i$'s such that
\begin{align}
	a_j := 
	\begin{cases}
	 o_j \text{ for } j = 1,2 \\
	 u_{j-2} \text{ for } j = 3\dots 7 \\
	o_{j- 5} \text{ for } j = 8 \dots r+5.
	\end{cases}
\end{align}
Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
\begin{align}
	(i,j,k) \in C(r) \iff a_ia_ja_i = a_k.
\end{align}
The size of $C(r)$ is $r+3$. 
%We can also employ some ordering of $C(r)$ such that $C(r,j)$ is a unique tuple for 
%$j = 1 \dots r+3$.
In this way, the group $G_0$ can be presented by
\begin{align}
	G_0  = \ip{ \{a_i\}_{i=1}^{r+5} : C(r) }.
\end{align}

Then we define the group $G_1$.
\begin{definition}
The presentation of $G_1$ has order-$2$ generators:
\begin{align*}
	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f, g, \{h_{jk}\}_{(i,j,k) \in C(r)};
\end{align*}
and relations:
\begin{align*}
	&a_i = b_ic_i = fd_i = gv_i,&& fb_if =c_i &&\text{ for } i= 1 \dots r+5 \\
	&h_{jk}b_j c_k = e,&& d_ib_jd_i = c_k &&\text{ for all } (i,j,k) \in C(r).
\end{align*}
\end{definition}
Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
We introduce the generator $g$ so that later we can associate $f$ with $g$ in linear relations of the Magic Square game.
Such relations are important for the self-testing proof.
Two important properties of $G_1$ are given in propositions below.
The first property of $G_1$ was first proved in Lemma~$4.4$ of \cite{slofstra2017}.
\begin{proposition}
	The group $G_1$ embeds relation $x_ix_jx_i = x_k$ for all $(i,j,k) \in C(r)$.
\end{proposition}
\begin{proof}
	We first show that $d_i c_j d_i = b_k$, which is because
	\begin{align}
		d_i c_j d_i = d_i (f b_j f) d_i = f (d_i b_j d_i) f = f c_k f = b_k.
	\end{align}
	Then, we can prove that 
	\begin{align}
		a_i a_j a_i = f d_i b_j c_j f d_i = (f d_i b_j d_i f)(f d_i c_j d_i f) = (f c_k f)(f b_k f) = b_k c_k = a_k. 
	\end{align}
\end{proof}
\begin{proposition}
	In the group $G_1$, the generators $f$ and $g$ commute with $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We can check that
	\begin{align}
		fa_i f a_i = d_i d_i = e && g a_i g a_i = v_i v_i  = e,
	\end{align}
	for all $i = 1 \dots r+5$.
\end{proof}
Note that there are two types of conjugacy relations in $G_1$. One is of the form
$f b_i f = c_i$ for all $i = 1 \dots r+5$. The other one is of the form 
$d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
we are going to embed it into a different set of linear relations in $\Gamma$.

\begin{definition}
The presentation of $\Gamma$ has order-$2$ generators:
\begin{align*}
	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
	\{\{ k_{c,j} \}_{j=1}^6\}_{c \in C(r)},
\end{align*}
and relations:
\begin{itemize}
\item for all $i = 1 \dots r+5$:
\begin{align}
	&a_i = b_ic_i = f_0d_i = g_0v_i \\
	&g_2 a_i w_i = e \\
	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
\end{align}
which embed $f_0 b_i f_0 = c_i$;
\item for all $ c = (i,j,k) \in C(r)$:
\begin{align}
	&h_{jk}b_j c_k = e\\
	&d_i k_{c,1} f_2 = e && b_j f_2 k_{c,2} = e && k_{c,2} k_{c,3} k_{c,4} = e\\
	&d_i k_{c,4} k_{c,5} = e && c_k k_{c,5} k_{c,6} =e && k_{c,1} k_{c,3} k_{c,6} = e,
\end{align}
which embed $d_i b_j d_i = c_k$;
\item relations of a Magic Square test:
\begin{align}
	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
\end{align}
which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
\item $J$ commutes with all the other generators.
\end{itemize}
\end{definition}
The special properties of the generators of $\Gamma$ are summarized in the two propositions below.
\begin{proposition}
	The group $\Gamma$ embeds all the conjugacy relations of $G_1$.
	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
\end{proposition}
The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
\begin{proposition}
	In the group $\Gamma$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
\end{proof}

%------------------------------------------------------------------------
\subsection{The representation of $\Gamma$}
%------------------------------------------------------------------------
In this section we give the presentation of $\Gamma$ which is built upon the representation 
$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma$ to construct the
ideal strategy that realizes our correlation.

Before giving the representation, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
of the representations,
\begin{align}
	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
\end{align}
Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
modulo $d$ implicitly. We use the second form of the basis when it is convenient.
We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
On the Hilbert space $W_2$, we define
\begin{align}
	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
\end{align}
\begin{definition}
The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
\begin{align}
	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
\end{align}
where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
\begin{align}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
\end{align}
The representation of the rest of the generators
can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
conjugation relations.
\end{definition}
We can check that
\begin{align}
	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
\end{align}
which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.

Following the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}, we construct a representation of $G_1$.
\begin{definition}
The representation $\Psi_1$ of $G_1$ on $W_2 \x W_{d-1}$ is defined by
\begin{itemize}
\item for $f_0$ and $g_0$
\begin{align}
	&\Psi_1(f_0) = X_{W_2} \x \1_{W_{d-1}} \\
	&\Psi_1(g_0) = Z_{W_2} \x \1_{W_{d-1}},
\end{align}
\item
for $i = 1 \dots r+5$,
\begin{align}
	&\Psi_1(a_i) = \1_{W_2} \x \Psi_0(a_i) \\
	&\Psi_1(b_i) = \ketbra{x_1}{x_1} \x \Psi_1(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
	&\Psi_1(c_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(a_i) \\
	&\Psi_1(d_i) =  X_{W_2} \x \Psi_0(a_i)\\
	&\Psi_1(v_i) = Z_{W_2} \x \Psi_0(a_i).
\end{align}
\item for $(i,j,k) \in C(r)$,
\begin{align}
	\Psi_1(h_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(a_j) + \ketbra{x_2}{x_2} \x \Psi_1(a_k).
\end{align}
\end{itemize}
\end{definition}
